
%% 1-2 pages

\section{Discussion}

This study aims to improve the managements and communication of technical debt in software development projects by introducing a visualization tool.
A concept of the visualization tool was developed using concept driven design research and an interactive prototype of the tool was designed and evaluated in order to answer the question: 
\textbf{Can a visualization tool help software development teams manage technical debt by improving awareness and communication about technical debt strategy and priorities?}

The findings from the study suggests that a visualization tool can improve the communication and management of technical debt, a majority of participants in the study thought a tool like the prototype would improve communication about technical debt and make management easier.
However, the study also finds that since technical debt always exists in the broader context of a project and a business with many competing priorities, technical debt management can be complex and can not be isolated from the rest of the development process.

In order to answer the main research question stated above, the prototype was evaluated based on two sub-questions.
The first question, \textit{Does the prototype present enough information for developers to make decisions about if and when to pay off technical debt?}, focused on the information provided by the prototype.
In general the participants did find the information provided in the prototype adequate, with one main exclusion being a metric of the cost and benefit of paying off each debt item.
Some participants did note that this information probably would be hard to define since there is no obvious unit in which to measure this.
A suggestion from one participant was to provide a basic scale from 1-5 to assign as a cost vs benefit metric to each debt item and let each development team decide for themselves what this scale implicates.
Another similar approach proposed by Seaman and Guo would be to enable a cost-benefit analysis borrowed from financial debt by including \textit{principal} and \textit{interest} estimates for each debt item \cite{seaman_using_2012}.
This would make it possible to compare and easily prioritize debt items as well as aid in planning, which multiple participants raised as a concern without proper estimates of time to pay off each item.

The second sub-question, \textit{Can the prototype help improve awareness about technical debt strategy and priorities withing a software development team?}, aims to help answer whether the prototype can help teams align on priorities and decisions and improve communication.
A theme that emerged from the interview was that without a designated forum and platform to record and structure discussions about technical debt, they tend to happen casually among developers in the day to day work.
It is of course not a bad thing to have these daily discussions among developers, but if the communication and decisions about technical debt never gets recorded or formally agreed upon by the team as a whole, it is hard to follow up and keep track of the accumulated debt.

According the the results from this study, a tool like the one proposed by this paper could be both a place to record and structure the teams strategy regarding technical debt, but also a tool to inform the team and make sure that everyone involved in a project are aware of the progress and priorities regarding debt.
Many participants said that this would be a very valuable tool to use in sprint planning meetings to update the team on the current status of debt in the project and agree on what to do next regarding technical debt.
It was also suggested that the tool could be used as a means of communication between developers and management with regards to budget, new features and long term project planning.

Further, regarding the visualizations presented in the prototype, even though a large majority of the participants did think the visualizations provided valuable information, there are some notable critique of the interface.
The debt type and timeline widgets were overall accepted without major objections.
However, the overview icicle plot did receive mixed opinions from the participants in the study, most notably that it would not fully capture all aspects and parts of a large software project, since it only represents the source code of a single repository.
This, in turn, does make it far less useful since it only provides an overview of a subsection of the possible technical debt in a project.
The combination of the breadth of technical debt problems that might arise and the complexity of large software architectures, a single visualization simply will not be enough.

One possible solution would be to remove the possibility to assign a debt item to a location in the project, and focus on providing visualization for the other properties of technical debt such as severity, cost and timeline.
With that said, the results in this study does show that the idea of providing an overview of the location does add value to the tool, and a better solution would be to explore the possibility to expand the interaction of the overview visualization and add more views and possibly more layers.
Since the different debt types operate on different "levels", where for example architectural debt might include several micro services and span multiple code bases and code debt often affects only a couple of lines of code in a specific file, a multi layer visualization could allow for the user to zoom into the visualization and be presented with details for the relevant type of debt on each level.
Furthermore, another point noted by the participants were the ability to view multiple source code repositories at the same time to manage debt for multiple projects together.
In order to provide this functionality, it would be of interest to investigate the possibility of implementing some of the techniques from the survey of multiple tree visualizations by Graham and Kennedy \cite{graham_survey_2010}.

\input{Sections/Subsections/MethodCritique}
\input{Sections/Subsections/FutureWork}